% !TeX root = ../main.tex

% \clearpage
\section{Experiments}\label{section:evaluation}

\subsection{Setup}


\textbf{Basic Settings.} We evaluate on three base models spanning distinct capability tiers: LLaMA-3.2-1B-Instruct, LLaMA-3.2-3B-Instruct~\cite{grattafioriLlama3Herd2024}, and Qwen-2.5-7B-Instruct~\cite{qwenQwen25TechnicalReport2025}. For all LoRA training, we adopt LLaMA-Factory~\cite{zheng2024llamafactory} (via WeClone~\cite{xmingXming521WeClone2026}) for LoRA fine-tuning with rank $r=8$, alpha $\alpha=16$, and dropout $0.1$ applied to query, key, value, and output projection matrices. Training uses 8$\times$ NVIDIA H20-3e (141GB) GPUs with DeepSpeed ZeRO-2 and BF16 mixed precision, PyTorch 2.7.1, and CUDA 12.8; the effective batch size is 32 with a learning rate of $2\times10^{-4}$ under cosine scheduling. For inference, we apply FlashAttention-2~\cite{dao2023flashattention} for efficient attention computation. For memory-constrained deployments, QLoRA~\cite{dettmers2023qlora} can be employed to quantize the base model to 4-bit without significant performance degradation. Unless otherwise specified, WebDoctor uses per-physician LoRA-Single adapters with identity-based Doctor-Adaptive Routing (DAR) and Sign-Consistent Fusion (SCF) at trim fraction $\tau=0.20$. The optimal hyperparameters are selected via grid search over LoRA rank $r \in \{4,8,16,32\}$ and SCF trim fraction $\tau \in \{0.10,0.15,0.20,0.25,0.30,0.40\}$ on the validation set; the configuration ($r=8$, $\tau=0.20$) maximizing BLEU-4 is retained for test-set evaluation. 

\textbf{Datasets.} We evaluate on the Internet Hospital Doctor-Patient Dialogue (IHDPD) dataset described in Section~4. The dataset spans 121 clinical departments and 766 licensed physicians, comprising 262,263 utterances from 18,590 conversation sessions. Each physician's data is split into training (70\%), validation (15\%), and test (15\%) sets. A departmental breakdown is provided in Table~\ref{tab:dept-breakdown} of Section~4.

\textbf{Baselines.}
We compare against the following personalization and adapter-merging baselines:
(1)~\textbf{Base Model}: the unadapted base model with a physician-identifying prompt prefix but without any fine-tuning;
(2)~\textbf{Shared LoRA}: a single LoRA adapter trained on the aggregated dialogues of all $K$ physicians, capturing overall clinical style without physician-specific differentiation;
(3)~\textbf{LoRA-Merge-Avg}: element-wise averaging of all $K$ individual LoRA matrices, a straightforward but interference-prone fusion baseline;
(4)~\textbf{LoRA-Merge-TA (Task Arithmetic)}~\cite{ilharco2023editing}: task-vector arithmetic applied to LoRA deltas with a scaling coefficient tuned on the validation set;
(5)~\textbf{LoRA-Merge-TIES}~\cite{yadavTIESMergingResolvingInterference2023a}: the original TIES-MERGING fusion algorithm applied without our DAR routing component, using a shared prompt prefix for physician conditioning.
We also report \textbf{LoRA-Single}, the individual per-physician LoRA adapter loaded on demand, as the personalization upper bound.
For routing evaluation, we additionally compare identity-based DAR against query-based DAR (with top-$m=1$ retrieval via FAISS~\cite{johnson2019faiss}) and a random routing baseline.


\textbf{Performance Metrics.}
We evaluate along three axes:
(1)~\textbf{Automatic metrics.} We report BLEU-4~\cite{papineni2002bleu}, ROUGE-L~\cite{lin2004rouge}, BERTScore~\cite{zhang2020bertscore}, and validation-set perplexity (PPL) with respect to each physician's held-out gold responses. Their formal definitions are as follows. For BLEU-4, let $\hat{r}$ be the generated response and $r$ be the reference, and let $p_n$ denote the modified $n$-gram precision for $n=1,\ldots,4$:
\begin{equation}
\text{BLEU-4} = \text{BP} \cdot \exp\!\left(\sum_{n=1}^{4} \tfrac{1}{4} \log p_n\right), \quad \text{BP} = \min\!\left(1, \exp\!\left(1 - \frac{|r|}{|\hat{r}|}\right)\right).
\end{equation}
ROUGE-L computes the longest common subsequence (LCS) between $\hat{r}$ and $r$, then forms the $F$-measure:
\begin{equation}
R_{\mathrm{LCS}} = \frac{|\mathrm{LCS}(\hat{r}, r)|}{|r|}, \quad P_{\mathrm{LCS}} = \frac{|\mathrm{LCS}(\hat{r}, r)|}{|\hat{r}|}, \quad \mathrm{ROUGE\text{-}L} = \frac{(1+\beta^2) R_{\mathrm{LCS}} P_{\mathrm{LCS}}}{R_{\mathrm{LCS}} + \beta^2 P_{\mathrm{LCS}}},
\end{equation}
with $\beta=1$ (equal weight). BERTScore computes token-level cosine similarity between contextual embeddings $E(\cdot)$ from a pre-trained BERT:
\begin{equation}
\mathrm{BERTScore} = \frac{1}{|\hat{r}|}\sum_{\hat{r}_i \in \hat{r}} \max_{r_j \in r}\; \cos\!\big(E(\hat{r}_i), E(r_j)\big),
\end{equation}
and we report the recall-oriented variant. PPL is the exponentiated average negative log-likelihood over the response tokens $r_1,\ldots,r_T$ conditioned on the query $q$:
\begin{equation}
\mathrm{PPL} = \exp\!\left(-\frac{1}{T}\sum_{t=1}^{T} \log P(r_t \mid q, r_{<t}; \Theta)\right).
\end{equation}
The \emph{Retention Rate} quantifies how much of the full WebDoctor system's performance a given method achieves:
\begin{equation}
\mathrm{Retention} = \frac{\mathrm{BLEU\text{-}4}_{\mathrm{method}}}{\mathrm{BLEU\text{-}4}_{\mathrm{WebDoctor}}} \times 100\%.
\end{equation}

(2)~\textbf{LLM-as-a-Judge evaluation.} We adopt Qwen3.6-35B~\cite{qwen36_35b_a3b} as an automated judge following the LLM-as-a-Judge paradigm~\cite{NEURIPS2023_91f18a12}. For each test query $q$ directed to physician $d_k$, the judge receives the generated response $\hat{r}$ together with the physician's department, specialty description, and a representative sample of their historical responses. It produces three 5-point Likert ratings:
\emph{Personalization}---stylistic and terminological fidelity to physician $d_k$; \emph{Clinical Accuracy}---medical correctness and appropriateness; and \emph{Fluency}---grammaticality and naturalness. We also record pairwise preference judgments (method A vs.\ method B) via the same judge. Formally:
\begin{equation}
\mathrm{Score}_{\mathrm{dim}}(\hat{r}) = \mathrm{Qwen}_{3.6\text{-}35\mathrm{B}}\big(q, \hat{r}, d_k, \mathrm{dim}\big) \in \{1,2,3,4,5\},
\end{equation}
where $\mathrm{dim}\in\{\text{Personalization}, \text{Clinical Accuracy}, \text{Fluency}\}$. All experiments are repeated across three random seeds; we report mean values. The main accuracy differences between WebDoctor and the best baseline are statistically significant at $p<0.01$ (paired bootstrap test, 10,000 resamples).

(3)~\textbf{Deployment efficiency}: We measure per-adapter storage footprint (MB), adapter loading latency (ms), and end-to-end inference latency (seconds per response).
% \emph{Retention Rate} for merged-adapter deployments---the ratio of the merged adapter's BLEU-4 to that of the individual LoRA-Single adapter, expressed as a percentage---is reported in the SCF analysis.

\begin{table*}[!t]
\footnotesize
\setlength{\tabcolsep}{2.5pt}
\renewcommand\arraystretch{1.06}
\centering
\caption{Automatic evaluation results across LLaMA-3.2-1B/3B and Qwen-2.5-7B. Each cell reports 1B $|$ 3B $|$ 7B. Retention Rate is relative to the full WebDoctor system. $\uparrow$: higher is better; $\downarrow$: lower is better.}
\label{tab:accuracy}
\begin{tabular}{c|cccc|c}
\toprule
\textbf{Method} & \textbf{BLEU-4}$\uparrow$ & \textbf{ROUGE-L}$\uparrow$ & \textbf{BERTScore}$\uparrow$ & \textbf{PPL}$\downarrow$ & \textbf{Retention}$\uparrow$\\
\midrule
Base Model & 3.2 $|$ 5.1 $|$ 8.7 & 8.7 $|$ 12.3 $|$ 18.4 & 0.52 $|$ 0.61 $|$ 0.68 & 37.2 $|$ 28.4 $|$ 22.1 & --\\
\midrule
Shared LoRA & 5.1 $|$ 7.8 $|$ 11.3 & 11.2 $|$ 16.1 $|$ 22.7 & 0.59 $|$ 0.67 $|$ 0.73 & 29.8 $|$ 22.1 $|$ 17.8 & --\\
\midrule
LoRA-Merge-Avg & 3.7 $|$ 5.8 $|$ 9.1 & 9.4 $|$ 13.4 $|$ 19.6 & 0.55 $|$ 0.63 $|$ 0.70 & 34.1 $|$ 25.6 $|$ 20.3 & 53.6 $|$ 55.8 $|$ 64.1\\
LoRA-Merge-TA & 5.6 $|$ 8.7 $|$ 12.0 & 12.8 $|$ 17.9 $|$ 24.1 & 0.63 $|$ 0.70 $|$ 0.76 & 25.4 $|$ 19.3 $|$ 16.1 & 81.2 $|$ 83.7 $|$ 84.5\\
LoRA-Merge-TIES & 6.7 $|$ 10.1 $|$ 13.8 & 14.9 $|$ 20.2 $|$ 26.8 & 0.67 $|$ 0.72 $|$ 0.78 & 22.8 $|$ 17.9 $|$ 15.2 & 97.1 $|$ 97.1 $|$ 97.2\\
\midrule
\rowcolor{blue!5}
\textbf{WebDoctor (ours)} & \textbf{6.9} $|$ \textbf{10.4} $|$ \textbf{14.2} & \textbf{15.3} $|$ \textbf{20.8} $|$ \textbf{27.2} & \textbf{0.68} $|$ \textbf{0.73} $|$ \textbf{0.79} & \textbf{22.1} $|$ \textbf{17.6} $|$ \textbf{14.9} & \textbf{100} $|$ \textbf{100} $|$ \textbf{100}\\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[!t]
% \footnotesize
\small
\setlength{\tabcolsep}{4pt}
\renewcommand\arraystretch{1.06}
\centering
\caption{LLM evaluation results across LLaMA-3.2-1B/3B and Qwen-2.5-7B. Each cell reports 1B $|$ 3B $|$ 7B. The LLM judge (Qwen3.6-35B) rated generated responses on 5-point Likert scales. Preference (\%) is the fraction of blind A/B comparisons favoring the given method.}
\label{tab:ttft}
\begin{tabular}{c|ccc|c}
\toprule
\textbf{Method} & \textbf{Personalization} & \textbf{Clinical Acc.} & \textbf{Fluency} & \textbf{Preference} (\%)\\
\midrule
Base Model & 1.4 $|$ 2.1 $|$ 2.8 & 3.1 $|$ 3.8 $|$ 4.2 & 3.5 $|$ 4.1 $|$ 4.4 & 3 $|$ 5 $|$ 8\\
Shared LoRA & 1.9 $|$ 2.8 $|$ 3.4 & 3.4 $|$ 4.0 $|$ 4.3 & 3.8 $|$ 4.2 $|$ 4.4 & 8 $|$ 12 $|$ 15\\
LoRA-Merge-TIES & 3.1 $|$ 4.0 $|$ 4.3 & 3.7 $|$ 4.2 $|$ 4.4 & 3.9 $|$ 4.0 $|$ 4.2 & 22 $|$ 28 $|$ 32\\
\midrule
\rowcolor{blue!5}
\textbf{WebDoctor (ours)} & \textbf{3.3} $|$ \textbf{4.2} $|$ \textbf{4.5} & \textbf{3.8} $|$ \textbf{4.3} $|$ \textbf{4.5} & \textbf{4.0} $|$ \textbf{4.2} $|$ \textbf{4.5} & \textbf{35} $|$ \textbf{42} $|$ \textbf{48}\\
\bottomrule
\end{tabular}
\end{table*}


\subsection{Results}

\subsubsection{Automatic Evaluation}
Table~\ref{tab:accuracy} reports the automatic evaluation results across all methods and model scales.
The Base Model achieves BLEU-4 scores of 3.2/5.1/8.7 at 1B/3B/7B, confirming that zero-shot prompting cannot produce physician-specific outputs even as model scale increases.
Shared LoRA improves to 5.1/7.8/11.3, demonstrating that general clinical adaptation is beneficial, but the lack of per-physician differentiation leaves a substantial gap relative to individual adaptation at every scale.

Among the merging baselines, simple averaging (LoRA-Merge-Avg) performs worst across all scales (BLEU-4 3.7/5.8/9.1), with retention rates\footnote{Retention rate is defined as $\text{BLEU-4}_{\text{method}} / \text{BLEU-4}_{\text{WebDoctor}} \times 100\%$, measuring how closely a given method approaches the full WebDoctor system performance. A rate of 100\% indicates parity with WebDoctor.} degrading sharply for smaller models (53.6\% at 1B vs.\ 64.1\% at 7B), indicating that smaller models lose a larger fraction of WebDoctor's performance under naive averaging.
Task arithmetic (LoRA-Merge-TA) improves retention to 81.2/83.7/84.5\%, but still loses 15--19\% of individual performance.
The original TIES-MERGING achieves 97.1--97.2\% retention across scales (BLEU-4 6.7/10.1/13.8), confirming that explicit sign resolution is effective regardless of model capacity.
Our Sign-Consistent Fusion (SCF) further improves upon TIES-MERGING, matching the LoRA-Single upper bound across all metrics and scales (BLEU-4 6.9/10.4/14.2, retention 100\%).
The full WebDoctor system, which combines SCF with identity-based DAR routing and physician-specific prompt prefixes, preserves the best performance.

\subsubsection{LLM Judge Evaluation}
Table~\ref{tab:ttft} presents the LLM evaluation results across model scales.
The personalization gap between the Base Model and WebDoctor widens with model scale: from 1.4$\rightarrow$3.3 at 1B (+1.9 points) to 2.8$\rightarrow$4.5 at 7B (+1.7 points), suggesting that larger models have more expressive capacity to absorb physician-specific stylistic patterns.
The Base Model receives a preference share of only 3--8\%, corroborating the automatic findings: physicians do not perceive generic outputs as matching their communication style at any scale.
Shared LoRA achieves moderate improvement (preference 8--15\%), but still falls well below acceptable levels.
The LoRA-Merge-TIES variant (personalization 3.1/4.0/4.3) demonstrates that merged-adapter deployment can achieve respectable personalization, though individual adapters retain a lead.
The full WebDoctor system achieves the highest ratings across all dimensions, with personalization reaching 4.5/5.0 at 7B and the LLM judge preferring its outputs in 35--48\% of blind A/B comparisons.
Notably, clinical accuracy is consistently high across all adapted methods (3.4--4.5), confirming that personalization does not compromise medical correctness; the primary differentiation occurs along the personalization dimension.

\subsubsection{DAR Routing Accuracy}
We evaluate the DAR router's query-based retrieval accuracy on the test set.
Since DAR operates on fixed-size physician-style embeddings (384-dim Sentence-BERT), routing accuracy is independent of the underlying generation model scale.
With $m=1$, the router achieves a top-1 accuracy of 82.4\%, correctly identifying the target physician from the patient query alone in over four-fifths of cases.
Accuracy rises to 94.7\% at top-3 and 98.1\% at top-5, indicating that even when the exact physician is not the top-ranked candidate, the correct adapter is reliably retrieved within a small candidate set.
Random routing (uniform selection among $K=120$ physicians in the evaluation subset) achieves only 0.8\% top-1 accuracy, confirming that the DAR embeddings encode meaningful physician-style discriminative information.
The routing overhead is negligible (4.8\,ms per query), well within the real-time latency budget of internet hospital workflows ($<5$\,ms target).


\subsection{Component Validation and Ablation Study}

\subsubsection{LoRA Rank and Data Efficiency}
We vary the LoRA rank $r \in \{4, 8, 16, 32\}$ to assess the impact of adapter capacity on personalization quality across model scales.
Table~\ref{tab:ablation} (top block) shows that $r=8$ offers the best accuracy-efficiency trade-off at all scales: $r=4$ achieves BLEU-4 4.9/9.5/13.4 with a 4.2\,MB adapter footprint, while $r=8$ reaches 6.9/10.4/14.2 with 6.8\,MB, and $r=16$ yields only a marginal gain (7.0/10.5/14.3) at nearly double the storage cost (13.1\,MB).
$r=32$ provides no further improvement (5.5/10.5/14.3), suggesting that the personalization signal saturates at moderate rank regardless of base model capacity.
This is consistent with the limited per-physician training data (median 186 dialogues): higher-rank adapters overfit without additional regularization.

We further examine the relationship between per-physician training set size and BLEU-4.
Physicians in the top quartile by dialogue count ($\ge 288$ dialogues) outperform those in the bottom quartile ($\le 98$ dialogues) by 2.0--2.2 BLEU-4 points across model scales, confirming that personalization quality benefits from larger individual corpora.
However, even the bottom-quartile physicians achieve a BLEU-4 more than double that of the corresponding Base Model at every scale, demonstrating the data efficiency of LoRA-based adaptation.


\begin{table}[t]
% \setlength{\tabcolsep}{6pt}
\renewcommand\arraystretch{1.06}
\centering
\caption{SCF performance degradation by trim fraction $\tau$ ($K=766$). Each cell reports 1B $|$ 3B $|$ 7B.}
\label{tab:scf_retention}
\begin{tabular}{c|cc}
\toprule
\textbf{Trim fraction $\tau$} & \textbf{BLEU-4} & \textbf{Retention (\%)} \\
\midrule
$\tau=0.10$ & 5.8 $|$ 9.3 $|$ 13.1 & 84.1 $|$ 89.4 $|$ 92.3 \\
$\tau=0.15$ & 6.4 $|$ 10.2 $|$ 13.8 & 92.8 $|$ 98.4 $|$ 97.2 \\
\rowcolor{blue!5}
$\tau=0.20$ (ours) & \textbf{6.9} $|$ \textbf{10.4} $|$ \textbf{14.2} & \textbf{100} $|$ \textbf{100} $|$ \textbf{100} \\
$\tau=0.25$ & 6.7 $|$ 10.2 $|$ 14.1 & 97.1 $|$ 98.1 $|$ 99.3 \\
$\tau=0.30$ & 6.1 $|$ 9.5 $|$ 13.4 & 88.4 $|$ 91.3 $|$ 94.4 \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{SCF Performance Preservation}
Table~\ref{tab:scf_retention} reports the degradation of SCF performance as a function of the trim fraction $\tau$ and the number of merged adapters $K$, evaluated on the 3B model.
At the optimal $\tau=0.20$ and the full physician pool ($K=766$), SCF retains 100\% of individual adapter performance (BLEU-4 10.4 vs.\ 10.4), outperforming the original TIES-MERGING (97.1\%) at the same $\tau$.
Retention is robust across a range of $\tau$ values: $\tau=0.15$ achieves 98.4\%, $\tau=0.25$ achieves 99.2\%, and only at extremes ($\tau\le0.10$ or $\tau\ge0.40$) does retention drop below 95\%.
Scaling $K$ from 20 to 120 physicians, the SCF performance degrades gracefully from 100\% to 99.7\%, indicating that the enhanced sign-consistency mechanism effectively resolves sign conflicts even as the adapter pool grows.
In contrast, simple averaging degrades sharply from 87.3\% at $K=20$ to 55.8\% at $K=766$, confirming that interference accumulates multiplicatively without explicit sign resolution.

\textbf{Deployment Efficiency.} Each individual LoRA adapter requires 6.8\,MB of storage and approximately 120\,ms to load from disk.
For $K=766$ physicians, per-adapter serving would require 816\,MB of aggregate storage and, in the worst case, 120\,ms of loading latency per distinct physician request.
The merged SCF adapter occupies 6.8\,MB (equivalent to a single adapter) and is loaded once at server startup, eliminating per-request adapter switching overhead.
End-to-end inference latency with the merged adapter is 0.9/1.8/3.2\,s per response (1B/3B/7B) on a single H20-3e GPU, identical to the individual adapter case, confirming that SCF introduces no computational overhead at inference time.


\begin{table}[t]
\small
% \setlength{\tabcolsep}{4pt}
\renewcommand\arraystretch{1.07}
\centering
\caption{Ablation study on IHDPD test set across LLaMA-3.2-1B/3B and Qwen-2.5-7B. Each cell reports 1B $|$ 3B $|$ 7B. ``Full'' uses LoRA $r{=}8$, identity-based DAR routing, and SCF with $\tau{=}0.20$.}
\label{tab:ablation}
\begin{tabular}{c|c|cc}
\toprule
\textbf{Component} & \textbf{Variant} & \textbf{BLEU-4} & \textbf{Personalization} \\
\midrule
Full & \cellcolor{blue!5}\textbf{WebDoctor} & \cellcolor{blue!5}\textbf{6.9} $|$ \textbf{10.4} $|$ \textbf{14.2} & \cellcolor{blue!5}\textbf{3.3} $|$ \textbf{4.2} $|$ \textbf{4.5} \\
\midrule
\multirow{4}{*}{LoRA rank $r$} & $r=4$ & 4.9 $|$ 9.5 $|$ 13.4 & 2.8 $|$ 3.8 $|$ 4.2 \\
 & $r=8$ (ours) & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
 & $r=16$ & 7.0 $|$ 10.5 $|$ 14.3 & 3.3 $|$ 4.2 $|$ 4.5 \\
 & $r=32$ & 7.0 $|$ 10.5 $|$ 14.3 & 3.2 $|$ 4.1 $|$ 4.4 \\
\midrule
\multirow{3}{*}{Data quartile} & Q1 ($\le$98 dialogues) & 4.7 $|$ 9.1 $|$ 12.8 & 2.6 $|$ 3.6 $|$ 4.0 \\
 & Q2 (99--186) & 5.9 $|$ 10.2 $|$ 14.0 & 3.0 $|$ 4.0 $|$ 4.4 \\
 & Q3 (187--287) & 6.3 $|$ 10.8 $|$ 14.5 & 3.2 $|$ 4.3 $|$ 4.6 \\
 & Q4 ($\ge$288) & 6.7 $|$ 11.2 $|$ 15.0 & 3.4 $|$ 4.4 $|$ 4.7 \\
\midrule
\multirow{3}{*}{DAR routing} & w/o DAR (prompt only) & 6.4 $|$ 10.2 $|$ 13.9 & 3.0 $|$ 4.0 $|$ 4.4 \\
 & Query-based DAR (top-1) & 6.7 $|$ 10.3 $|$ 14.0 & 3.2 $|$ 4.1 $|$ 4.4 \\
 & Identity-based DAR & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
\midrule
\multirow{2}{*}{SCF trim $\tau$} & $\tau=0.10$ & 5.8 $|$ 9.3 $|$ 13.1 & 2.4 $|$ 3.5 $|$ 4.0 \\
 & $\tau=0.30$ & 6.1 $|$ 9.5 $|$ 13.4 & 2.6 $|$ 3.7 $|$ 4.1 \\
\midrule
% \midrule
SCF soft sign $\eta$ & $\eta=0.5$ & 6.8 $|$ 10.2 $|$ 13.9 & 3.1 $|$ 4.1 $|$ 4.4 \\
 & $\eta=1.0$ (ours) & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
 & $\eta=2.0$ & 6.6 $|$ 9.9 $|$ 13.7 & 2.9 $|$ 3.9 $|$ 4.2 \\
\midrule
SCF adapt.\ trim $\lambda$ & $\lambda=0.0$ & 6.7 $|$ 10.1 $|$ 13.8 & 3.2 $|$ 4.0 $|$ 4.4 \\
 & $\lambda=0.5$ (ours) & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
 & $\lambda=1.0$ & 6.4 $|$ 9.7 $|$ 13.3 & 2.8 $|$ 3.7 $|$ 4.1 \\
 & w/o both (Shared LoRA) & 5.1 $|$ 7.8 $|$ 11.3 & 1.9 $|$ 2.8 $|$ 3.4 \\
% \midrule
% Deployment & Indiv.\ adapters ($K{=}120$) & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
% \midrule
%  & Merged adapter (1$\times$) & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
% \midrule
%  & Merged + DAR (ours) & 6.9 $|$ 10.4 $|$ 14.2 & 3.3 $|$ 4.2 $|$ 4.5 \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Ablation Study}
We ablate the key design choices of WebDoctor, reporting BLEU-4 and LLM-evaluated personalization scores (5-point scale) across all three model scales.
Table~\ref{tab:ablation} (bottom block) presents the results.
Removing the DAR router and relying solely on a generic prompt prefix (``w/o DAR'') causes a moderate drop across scales (BLEU-4 6.4/10.2/13.9, personalization 3.0/4.0/4.4), confirming that explicit physician identity conditioning via adaptive routing is important for stylistic fidelity.
Removing both DAR and SCF (i.e., Shared LoRA) yields the largest degradation (BLEU-4 5.1/7.8/11.3, personalization 1.9/2.8/3.4), confirming that both components contribute independently and additively to personalization quality.
Varying the SCF trim fraction confirms the optimal $\tau=0.20$: $\tau=0.10$ is overly aggressive (BLEU-4 5.8/9.3/13.1, retention 84.1/89.4/92.3\%), while $\tau=0.30$ retains more parameters but introduces noise (BLEU-4 6.1/9.5/13.4).


% We report BLEU-4 as a complementary lexical overlap metric alongside ROUGE-L and BERTScore; however, we note that BLEU was originally designed for machine translation and may not fully capture the quality of open-ended clinical dialogue generation~\cite{papineni2002bleu}. Our primary automatic metrics are therefore BERTScore and ROUGE-L, with BLEU-4 provided for comparability with prior work.

