% !TeX root = ../main.tex

\section{Introduction}

The rapid advancement of digital health technologies has propelled internet hospitals into a central role within modern healthcare delivery systems, particularly in regions with high patient-to-physician ratios~\cite{internet-hospital}. These platforms enable large-scale remote consultations, where patients submit textual descriptions of their symptoms and medical concerns, and licensed physicians respond with diagnostic guidance, treatment recommendations, and follow-up instructions. The doctor-patient dialogue generated in this setting constitutes a uniquely valuable corpus: it captures authentic clinical reasoning, physician-specific communication styles, and institutionally governed medical discourse at substantial scale.

Large language models (LLMs)~\cite{hu2023llama} have demonstrated remarkable capabilities across a wide range of natural language processing tasks, including clinical knowledge encoding~\cite{medical-llm} and medical dialogue generation~\cite{clinical-dialogue}. In the context of internet hospitals, deploying an LLM-based assistant to augment physicians during patient interactions holds significant promise: it can reduce documentation burden, suggest evidence-based responses, and improve the consistency of clinical communication. However, a critical limitation of current LLM deployment paradigms in healthcare settings is their tendency to produce \textit{generic, depersonalized} outputs. A single shared model, whether fine-tuned on aggregated clinical data or prompted with few-shot examples, cannot capture the nuanced linguistic preferences, departmental norms, specialty-specific terminology, and institutional policy constraints that distinguish one physician from another. This depersonalization undermines physician trust in AI-assisted tools and limits the practical adoption of LLMs in real-world clinical workflows~\cite{personalized-nlg}.

Personalizing language model outputs for individual users has been explored in the context of open-domain dialogue systems, where persona-conditioned generation aims to produce responses consistent with a predefined user profile~\cite{personalized-nlg}. However, adapting this paradigm to the clinical domain presents unique challenges. First, physician personalization must account for multiple overlapping constraints simultaneously: individual linguistic style (how a particular doctor phrases advice), departmental norms (what constitutes appropriate communication within a specialty such as cardiology versus dermatology), and institutional regulations (hospital-wide policies regarding disclaimers, referral protocols, and information disclosure). Second, the training data for each physician is inherently limited; a single doctor may only contribute a few hundred consultation records, making full model fine-tuning impractical and parameter-efficient approaches essential~\cite{hu2021lora,mangrulkar2022peft}. Third, the deployment environment demands efficient inference: loading hundreds of physician-specific models simultaneously is computationally prohibitive, necessitating intelligent routing and model merging strategies~\cite{yadav2024ties,lag2024,adapter-merging}.

In this paper, we propose a three-stage personalized adaptation framework that addresses these challenges through a novel combination of parameter-efficient fine-tuning, dynamic adapter routing, and interference-aware model merging. The framework comprises: (1) \textbf{Doctor-Specific LoRA Training}, wherein we leverage the weclone training pipeline~\cite{weclone} to train individual Low-Rank Adaptation (LoRA) modules for each physician using their historical consultation records. These lightweight adapters capture each doctor's distinct response patterns, linguistic habits, and domain-specific terminology preferences while maintaining a shared base model; (2) \textbf{LoRA-Augmented Generation (LAG) Routing}~\cite{lag2024}, which dynamically selects the appropriate doctor-specific LoRA adapter at inference time based on the context of the incoming patient query and the assigned physician's identity, ensuring that generated suggestions are stylistically and substantively aligned with the target doctor; and (3) \textbf{TIES-MERGING}~\cite{yadav2024ties}, which resolves parameter interference when fusing multiple doctor-specific LoRA adapters into a unified deployment artifact, enabling efficient multi-doctor serving without sacrificing personalization fidelity.

To support this research, we construct and release the \textbf{Internet Hospital Doctor-Patient Dialogue (IHDPD)} dataset, a de-identified multi-doctor multi-patient corpus collected from a real-world operational internet hospital. The dataset spans multiple clinical departments and encompasses diverse consultation scenarios, including initial symptom inquiry, follow-up management, medication guidance, and lifestyle counseling. All personal health information has been rigorously de-identified in compliance with institutional ethics protocols~\cite{deidentification}.

Our experimental evaluation demonstrates that the proposed framework achieves substantial improvements over competitive baselines across both automatic evaluation metrics and expert clinical human evaluation. Specifically, the LAG router achieves high routing accuracy, TIES-MERGING preserves a significant fraction of individual adapter performance post-fusion, and the end-to-end system generates responses that are consistently rated as more personalized, professional, and clinically appropriate by practicing physicians.

The remainder of this paper is organized as follows. Section~\ref{section:motivation} motivates the problem and surveys related work. Section~\ref{section:design} presents our proposed method in detail, covering LoRA training, LAG routing, and TIES-MERGING. Section~4 describes the implementation of the system, including dataset construction and training pipeline configuration. Section~\ref{section:evaluation} reports our experimental setup, evaluation metrics, and empirical results. Section~6 discusses the implications, limitations, and ethical considerations of our work. Section~7 concludes the paper and outlines directions for future research.
