% !TeX root = ../main.tex
\section{Discussion}
\subsection{Key Findings and Implications}

Our experimental results yield several notable findings. First, the substantial gap at the 3B scale between the Base Model (BLEU-4: 5.1, Personalization: 2.1) and LoRA-Single (BLEU-4: 10.4, Personalization: 4.2) confirms that physician-specific adaptation is both necessary and achievable. The base model, even when conditioned on physician-identifying prompt prefixes, fails to produce responses that physicians recognize as consistent with their own practice style. This finding has important implications for the deployment of LLMs in clinical settings: a one-size-fits-all model, no matter how capable, is unlikely to gain physician trust without personalization.

Second, the SCF results demonstrate that our enhanced merging preserves 100\% of individual adapter performance, improving over the original TIES-MERGING baseline (97.1\%) while reducing the deployment footprint from $K$ separate adapters to a single merged artifact. This represents a critical practical advance: internet hospitals seeking to serve hundreds of physicians can now do so with a single inference endpoint, dramatically simplifying infrastructure requirements and reducing operational costs. The superiority over simple averaging (55.8\% retention) and task arithmetic (83.7\% retention) validates the importance of explicit interference resolution in multi-adapter fusion.

Third, the DAR router contributes meaningful gains beyond straightforward identity-based routing, particularly in scenarios where the optimal physician adapter is not predetermined. While our experiments primarily evaluate the standard internet hospital setting (known target physician), the DAR capability opens avenues for automated triage and preliminary response generation in under-resourced settings.

\subsection{Limitations}

Several limitations of this work should be acknowledged. First, the IHDPD dataset is drawn from a single internet hospital in a specific geographic region, which may limit the generalizability of our findings to other healthcare systems with different clinical communication norms, languages, or regulatory environments. Future work should validate the framework across multiple institutions and languages.

Second, our personalization approach captures surface-level stylistic and terminological preferences but does not explicitly model deeper aspects of clinical reasoning, such as differential diagnosis pathways or treatment decision logic. The framework may therefore be less effective for physicians whose distinctive practice style is rooted in clinical decision-making patterns rather than linguistic expression.

Third, although SCF achieves 100\% retention at $\tau=0.20$, the original TIES-MERGING retains only 97.1\%, and the remaining gap under suboptimal $\tau$ still represents a measurable degradation from individual adapter performance. For physicians with highly idiosyncratic communication styles, the remaining 2.9\% gap may be perceptible. A hybrid deployment strategy---where outlier physicians retain individual adapters while the majority are served through the merged model---may represent a practical compromise.

Fourth, our evaluation relied on the LLM judge (Qwen3.6-35B-Instruct) for automated assessment; future work should incorporate independent physician evaluators. Larger-scale evaluation with more diverse clinical perspectives would strengthen the reliability of the personalization assessment.

\subsection{Ethical Considerations}

The deployment of personalized LLMs in clinical settings raises important ethical questions. While our framework aims to augment rather than replace physician judgment---the final decision to adopt, modify, or reject generated suggestions remains with the doctor---there is a risk that over-reliance on AI suggestions could erode clinical autonomy or introduce automation bias. Robust training on appropriate use and clear institutional policies governing AI assistance are essential complements to the technical system.

Additionally, the personalization mechanism raises questions about accountability: if a personalized model generates a suggestion that a physician adopts and that leads to an adverse outcome, where does responsibility lie? Our position is that physician-specific personalization, by making suggestions more recognizable and interpretable to the target doctor, may actually \textit{reduce} the risk of uncritical adoption compared to generic AI outputs, as physicians are better able to evaluate suggestions framed in their own clinical language. Nevertheless, clear governance frameworks are needed.

\subsection{Future Work}

Beyond addressing the limitations discussed above, several promising directions emerge from this work. The framework could be extended to incorporate multi-modal personalization signals, such as a physician's diagnostic imaging interpretation patterns or procedural documentation style. Continuous personalization, where LoRA adapters are updated incrementally as physicians generate new consultation records, could maintain personalization fidelity over time. Finally, the DAR router could be enhanced with reinforcement learning from physician feedback, creating a closed-loop system where routing decisions are optimized based on downstream adoption rates.
