% !TeX root = ../main.tex
\section{Related Work}\label{section:motivation}

The deployment of LLM-based clinical assistants in internet hospital settings presents a fundamental tension between the efficiency gains of automation and the personal nature of the doctor-patient relationship. In this section, we articulate the core motivations for doctor-specific personalization and situate our work within the broader research landscape.

\subsection{The Personalization Imperative in Clinical Communication}

Physician-patient communication is not a monolithic phenomenon. Doctors develop distinctive communication styles shaped by their clinical training, years of practice, specialty domain, and institutional culture. A cardiologist's response to a patient describing chest discomfort differs markedly from a dermatologist's discussion of a skin lesion---not only in clinical content but in linguistic register, use of technical versus lay terminology, degree of empathy expression, and inclusion of specialty-specific disclaimers and referral language. When an AI assistant generates suggestions that violate these unwritten norms, physicians experience friction: they must either extensively edit the suggestion (negating the efficiency benefit) or accept a response that feels inauthentic to their practice style (undermining trust).

Existing approaches to clinical NLP largely ignore this dimension of personalization. Medical dialogue systems trained on aggregated corpora~\cite{zengMedDialogLargescaleMedical2020} produce responses optimized for average performance across all clinicians, effectively erasing individual differences. While such models may achieve reasonable scores on automated metrics, their clinical utility is constrained by the ``last-mile'' problem of physician adoption~\cite{info:doi/10.2196/jmir.7854}. Our work is motivated by the hypothesis that \textit{physician-specific model adaptation, when implemented efficiently, can close this adoption gap} by producing suggestions that physicians recognize as consistent with their own voice and practice norms.

\subsection{Parameter-Efficient Fine-Tuning with LoRA}

Full fine-tuning of large language models for each individual physician is computationally prohibitive, particularly in hospital settings where dozens or hundreds of doctors may require personalized models. Low-Rank Adaptation (LoRA)~\cite{hu2021lora} addresses this challenge by freezing the pre-trained base model weights and injecting trainable low-rank decomposition matrices into the attention layers. This reduces the number of trainable parameters by several orders of magnitude while achieving competitive performance on downstream tasks. We adopt LoRA fine-tuning based on LLaMA-Factory~\cite{zheng2024llamafactory}, an efficient open-source framework that provides optimized kernels for training and inference.

Recent advances in parameter-efficient fine-tuning (PEFT)~\cite{peft} have introduced several adapter variants, including prefix tuning, prompt tuning, and IA$^3$. Among these, LoRA offers a favorable trade-off between adaptation quality and storage efficiency for our use case, as each doctor-specific adapter occupies only a few megabytes of storage and can be loaded and unloaded at inference time with minimal overhead.

\subsection{LoRA Routing and Augmented Generation}

When multiple LoRA adapters coexist---each tailored to a different physician---the system must determine which adapter to activate for a given incoming query. LoRA composition methods such as LoRAHub~\cite{huangLoraHubEfficientCrossTask2024} dynamically select and compose LoRA modules for downstream tasks. In our setting, the routing problem is simplified by the fact that the target physician is known at query time (the patient is consulting a specific doctor), but dynamic adapter selection provides a principled framework for generalizing to scenarios where the optimal adapter must be inferred from the query context alone, such as triage or automated preliminary response generation.

\subsection{Model Merging and Interference Resolution}

Deploying hundreds of individual LoRA adapters introduces operational complexity. An alternative is to merge multiple adapters into a single unified model, enabling a single inference endpoint to serve multiple physicians. However, naive parameter averaging often leads to destructive interference between adapters, where the merged model performs significantly worse than any individual adapter. TIES-MERGING~\cite{yadavTIESMergingResolvingInterference2023a} addresses this via three stages: (1) trimming low-magnitude parameter changes that may represent noise, (2) resolving sign conflicts through an elected sign mechanism, and (3) merging only the parameters that agree in sign direction. Our SCF method builds on this paradigm with enhanced sign-consistency mechanisms that further improve merging quality for large adapter pools. Task arithmetic~\cite{ilharco2023editing} provides an alternative formulation, but sign-resolved methods have been shown to outperform it when merging a larger number of task-specific models, making the approach particularly suitable for our multi-doctor scenario.

% \subsection{Positioning of This Work}

% To the best of our knowledge, this is the first work to systematically combine doctor-specific LoRA training, adaptive adapter routing, and sign-consistent model merging into a unified framework for personalized clinical response generation. While each component has been studied in isolation, their integration presents nontrivial engineering and research challenges: the LoRA modules must be trained with sufficient personalization signal from limited per-doctor data; the DAR router must operate with low latency in a production environment; and SCF must be adapted to the specific characteristics of LoRA parameter spaces in the clinical domain. We address these challenges through careful system design and empirical validation, as detailed in the following sections.
