\section*{Abstract}

Internet hospitals generate vast amounts of doctor-patient dialogues, yet existing LLM-based assistants produce generic, depersonalized outputs that fail to capture individual physicians' communication styles, leading to limited real-world adoption in the outpatient process of internet hospitals. We address this gap by proposing WebDoctor, a three-stage personalized LLM outpatient assistant framework. First, doctor-specific low-rank adaptation modules are trained via LoRA fine-tuning on each physician's consultation records, producing compact adapters that encode individual response patterns. Second, Doctor-Adaptive Routing (DAR) dynamically selects the appropriate adapter at inference time through identity-based or query-based retrieval. Third, Sign-Consistent Fusion (SCF), an interference-aware merging technique, consolidates multiple adapters into a unified deployment artifact while preserving individual adapter performance. We construct a real-world internet hospital doctor-patient dialogue (IHDPD) dataset spanning 121 clinical departments and 766 physicians. Evaluations with LLaMA-3.2-1B/3B and Qwen-2.5-7B demonstrate significant improvements over baselines. WebDoctor achieves BLEU-4 scores of 6.9/10.4/14.2 and personalization ratings of 3.3/4.2/4.5 at 1B/3B/7B, substantially above the corresponding base models (BLEU-4: 3.2/5.1/8.7; personalization: 1.4/2.1/2.8). WebDoctor offers a practical pathway toward trustworthy, physician-centered AI assistance in clinical workflows.


\clearpage
\newgeometry{top=0.85in,left=1in,right=1in,footskip=0.75in}
\linenumbers


